Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-22 paper/v2/paper-edited.tex
making references consistent
edits section 5.1, 5.2

The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator. In general, we employ the following distributivity equivalences:
%
\[
\begin{array}{c}
  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference. The compiler flags preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.

@@

% Formally define automata
%The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, \IE, route announcements flowing in the opposite direction. To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine on the reversed regular expression. Each automaton for the reversed regular expression of $r_i$ is a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
%
% Formally define product graph
The combined PGIR is a tuple ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon V' \times V'$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.

For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$, written as $\tilde{n} = l$, to indicate that the topology location for node $n$ is $l$. When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.

@@

% Formal product construction
Let $a_i$ and $b_i$ denote states in the regular policy automata.
The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
%
The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each regular expression matched in the current node.
% in preferences are achieved from each policy automaton for every node in the product construction.
%
Finally, there is an edge from each node in the PGIR such that $P(n) \neq \emptyset$ to the special end node $e$. We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.

@@

\para{Acknowledgements}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595.

>>>>

The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator. In general, we employ the following distributivity equivalences:
%
\[
\begin{array}{c}
  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
%
In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ and $t \cdot u$ is preferred. \sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
%
\sysname also rejects policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.

@@

% Formally define automata
%The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated --- route announcements flowing in the opposite direction. To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine for the reversed regular expression. An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
%
% Formally define product graph
The combined PGIR is a tuple ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon V' \times V'$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.

For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$. We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$. When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.

@@

% Formal product construction
Let $a_i$ and $b_i$ denote states in the regular policy automata.
The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
%
The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
% in preferences are achieved from each policy automaton for every node in the product construction.
%
Finally, there is an edge from each node in the PGIR such that $P(n) \neq \emptyset$ to the special end node $e$. We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.

@@

\para{Acknowledgements}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.
